---
title: "Homework 4"
author: "Xindi Lu"
date: "October 9, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

###Get Data
```{r}
library(tidyverse)

basic <- read_tsv("basic.tsv", na = "\\N", quote = '')

rating <- read_tsv("rating.tsv", na = "\\N", quote = '')

dat<-merge(basic,rating, by ="tconst")%>% filter(titleType == "movie") %>% 
  select(averageRating, startYear, runtimeMinutes, numVotes)

summary(dat)

```

###Question 1

###(a)Do you need any transformations?
```{r}

ggplot(dat, aes(x = startYear, y = averageRating)) + geom_point() + geom_smooth(method = "lm")
ggplot(dat, aes(x = runtimeMinutes, y = averageRating)) + geom_point() + geom_smooth(method = "lm")
ggplot(dat, aes(x = log10(runtimeMinutes), y = averageRating)) + geom_point() + geom_smooth(method = "lm")


# simplest model
lm1 <- lm(averageRating ~ startYear + runtimeMinutes, data = dat)
summary(lm1)

# You will have to make a number of modeling choices:
# (a) Do you need any transformations?

# model transforming runtimeMinutes
lm2 <- lm(averageRating ~ startYear + log10(runtimeMinutes), data = dat)
summary(lm2)

# model considering startYear as a factor (categorical variable)
lm3 <- lm(averageRating ~ runtimeMinutes + factor(startYear), data = dat)
summary(lm3)
plot(lm3)

lm4 <- lm(averageRating ~ log(runtimeMinutes) + factor(startYear), data = dat)
summary(lm4)

#data.2 <- data[data$runtimeMinutes < 1000,] 
#ggplot(data.2, aes(x =runtimeMinutes , y = averageRating)) + geom_point() + facet_wrap(~cut_number(startYear, n = 5)) + geom_smooth(method = "lm") + ylab("IMDB rating") + xlab("Length")
#ggplot(data.2, aes(x =startYear , y = averageRating)) + geom_point() + facet_wrap(~cut_number(runtimeMinutes, n = 5)) + geom_smooth(method = "lm") + ylab("IMDB rating") + xlab("Year")

```

Keep lm4, and need to log, since the modeling with log, its R-sqaured and adjusted R-squared is the largest

####(b)Should you it a linear model or something curved?

All of them is linear model, accoding to the lm line in the plots, it's almost a flat line

####(c)Is an additive model adequate?
```{r}
#GAM


```

####(d)Do you need to filter out or downweight tail values to prevent the fit from being dominated by outliers?

```{r}

boxplot(dat$runtimeMinutes)


dat.test<- dat
outliers <- boxplot(dat.test$runtimeMinutes, plot=FALSE)$out
dat.test[which(dat.test$runtimeMinutes %in% outliers),]

dat.nout<- dat.test[-which(dat.test$runtimeMinutes %in% outliers),]
boxplot(dat.nout$runtimeMinutes)


lm.nout <- lm(averageRating ~ log(runtimeMinutes) + factor(startYear), data = dat.nout)
summary(lm.nout)


```

Yes. Since the Adjusted R-squared is bigger, whihc indicates a better model.

####(e) Should you weight by number of votes?

```{r}

```



###2
```{r}

dat.nout %>% filter(startYear > 2003) %>% ggplot(aes(x = log10(runtimeMinutes), y = averageRating)) + geom_point() + 
  geom_smooth(method = "lm") + facet_wrap(~ startYear)

```

###3

```{r}

lm.new <- lm(averageRating ~ log(runtimeMinutes), data = dat.nout)
predicted <- predict(lm.new)

predic.test<-predict(lm4)

# then create the scatterplot, may need to install the scatterplot3d
library(scatterplot3d)
scatterplot3d(log10(dat.nout$runtimeMinutes), dat.nout$startYear, predicted, angle = 75)

```

