---
title: "Homework 4"
author: "Xindi Lu, Jingyu Xie"
date: "October 9, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

###Get Data
```{r}
library(tidyverse)
library(mgcv)
library(scatterplot3d)
library(lattice)

basic <- read_tsv("basic.tsv", na = "\\N", quote = '')

rating <- read_tsv("rating.tsv", na = "\\N", quote = '')

dat<-merge(basic,rating, by ="tconst")%>% filter(titleType == "movie") %>% 
  select(averageRating, startYear, runtimeMinutes, numVotes)

```

###Question 1

###(a)Do you need any transformations?
```{r}

ggplot(dat, aes(x = startYear, y = averageRating)) + geom_point() + geom_smooth(method = "lm")
ggplot(dat, aes(x = runtimeMinutes, y = averageRating)) + geom_point() + geom_smooth(method = "lm")
ggplot(dat, aes(x = log10(runtimeMinutes), y = averageRating)) + geom_point() + geom_smooth(method = "lm")


# simplest model
lm1 <- lm(averageRating ~ startYear + runtimeMinutes, data = dat)
summary(lm1)

# You will have to make a number of modeling choices:
# (a) Do you need any transformations?

# model transforming runtimeMinutes
lm2 <- lm(averageRating ~ startYear + log10(runtimeMinutes), data = dat)
summary(lm2)

# model considering startYear as a factor (categorical variable)
lm3 <- lm(averageRating ~ runtimeMinutes + factor(startYear), data = dat)
summary(lm3)
plot(lm3)

lm4 <- lm(averageRating ~ log(runtimeMinutes) + factor(startYear), data = dat.nout)
summary(lm4)


ggplot(dat.nout, aes(x = log10(runtimeMinutes) , y = averageRating)) + geom_point() + facet_wrap(~cut_number(startYear, n = 5)) + geom_smooth(method = "lm") + ylab("IMDB rating") + xlab("Length")
ggplot(dat.nout, aes(x = startYear , y = averageRating)) + geom_point() + facet_wrap(~cut_number(runtimeMinutes, n = 5)) + geom_smooth(method = "lm") + ylab("IMDB rating") + xlab("Year")
```

```{r}
outliers <- boxplot(dat$runtimeMinutes, plot=FALSE)$out
dat[which(dat$runtimeMinutes %in% outliers),]

dat.nout<- dat[-which(dat$runtimeMinutes %in% outliers),]
```



According to the ggplot of IMDB ratings over lenght of movies, we notice that most of the observations are gathered in the left corner of the graph. Therefore, we decide to take log10 of length to make the relationship more obvious to check.

####(b)Should you it a linear model or something curved?

All of them is linear model, accoding to the lm line in the plots, it's almost a flat line

####(c)Is an additive model adequate?
```{r}
#GAM
IMDB.gam <- gam(averageRating ~ factor(startYear) + log(runtimeMinutes), data = dat.nout)
summary(IMDB.gam)
```

####(d)Do you need to filter out or downweight tail values to prevent the fit from being dominated by outliers?


Yes. Since the Adjusted R-squared is bigger, whihc indicates a better model.

####(e) Should you weight by number of votes?

```{r}

ggplot(dat.nout, aes(x = startYear , y =averageRating  )) + geom_point(aes(size = numVotes)) + scale_size_area() + geom_smooth(method.args = list(degree = 1), color = 'orange', se = FALSE) + geom_smooth(aes(weight = numVotes), method.args = list(degree = 1), se = FALSE)

ggplot(dat.nout, aes(x = log10(runtimeMinutes) , y =averageRating  )) + geom_point(aes(size = numVotes)) + scale_size_area() + geom_smooth(method.args = list(degree = 1), color = 'orange', se = FALSE) + geom_smooth(aes(weight = numVotes), method.args = list(degree = 1), se = FALSE)
```

According to the weighting plot,

###2
```{r}

dat.nout %>% filter(startYear >= 2000) %>% ggplot(aes(x = runtimeMinutes, y = averageRating)) + geom_point() + 
  geom_smooth(method = "lm") + facet_wrap(~ startYear)

```

###3

```{r}
dat.nna<- dat.nout[complete.cases(dat.nout), ]

IMDB.predict = predict(IMDB.gam, newdata = dat.nna)
IMDB.df = data.frame(dat.nna, fit = as.vector(IMDB.predict))

cloud(averageRating ~ runtimeMinutes * startYear, data = IMDB.df)

wireframe(fit ~ runtimeMinutes * startYear, data = IMDB.df,  drape = TRUE)
```

